Parameters estimation via HOSVD

### 2024-12-29 Code/R/Research/HOSVD parameters estimate.Rmd
Text edits

@@

rate1.rrmse <- matrix(numeric(len.out * 3), nrow = len.out)
rate2.rrmse <- matrix(numeric(len.out * 3), nrow = len.out)
freq1.rrmse <- matrix(numeric(len.out * 3), nrow = len.out)
freq2.rrmse <- matrix(numeric(len.out * 3), nrow = len.out)

@@

for (j in seq(len.out)) {
  pars.tssa <- rep(list(list(
    rate1 = numeric(R),
    rate2 = numeric(R),
    freq1 = numeric(R),
    freq2 = numeric(R)
  )), 3)

@@

    for (d in seq_along(trunc_dims)) {
      par.tssa <- tens_esprit(x,
                              I,
                              L,
                              groups = groups,
                              est_dim = d,
                              status = FALSE)

@@

  for (d in 1:3) {
    rate1.rrmse[j, d] <- rrmse(rates.true[1], pars.tssa[[d]]$rate1)
    rate2.rrmse[j, d] <- rrmse(rates.true[2], pars.tssa[[d]]$rate2)
    freq1.rrmse[j, d] <- rrmse(freqs.true[1], pars.tssa[[d]]$freq1)
    freq2.rrmse[j, d] <- rrmse(freqs.true[2], pars.tssa[[d]]$freq2)
  }
}

>>>>

groups <- list(1:2)
max.r <- max(sapply(groups, max))
est.dims <- list(1, 2, 3)

@@

rate1.rrmse <- matrix(numeric(len.out * length(est.dims)), nrow = len.out)
rate2.rrmse <- matrix(numeric(len.out * length(est.dims)), nrow = len.out)
freq1.rrmse <- matrix(numeric(len.out * length(est.dims)), nrow = len.out)
freq2.rrmse <- matrix(numeric(len.out * length(est.dims)), nrow = len.out)

@@

for (j in seq(len.out)) {
  pars.tssa <- rep(list(list(
    rate1 = numeric(R),
    rate2 = numeric(R),
    freq1 = numeric(R),
    freq2 = numeric(R)
  )), length(est.dims))

@@

    for (d in seq_along(est.dims)) {
      par.tssa <- tens_esprit(x,
                              I,
                              L,
                              groups = groups,
                              est_dim = d,
                              decomp = "HOSVD",
                              status = FALSE)

@@

  for (d in seq_along(est.dims)) {
    rate1.rrmse[j, d] <- rrmse(rates.true[1], pars.tssa[[d]]$rate1)
    rate2.rrmse[j, d] <- rrmse(rates.true[2], pars.tssa[[d]]$rate2)
    freq1.rrmse[j, d] <- rrmse(freqs.true[1], pars.tssa[[d]]$freq1)
    freq2.rrmse[j, d] <- rrmse(freqs.true[2], pars.tssa[[d]]$freq2)
  }
}
